Winter 2025 ToDo

### 2025-12-03 Relations/Paper/Summer_2025_TODO.tex
Todo update

    \item (Review 1) Elaborate on our motivations in the introduction (reviewer wasn't sure how relevant this is to ARS theory itself/ sees it as too minor a contribution.)

@@

    \item (Review 2) Unconvinced by the motivations for the project, believes the same can be achieved in a classical framework. So maybe we should explain our motivations more clearly.

>>>>

    \item [\done] (Review 1) Elaborate on our motivations in the introduction (reviewer wasn't sure how relevant this is to ARS theory itself/ sees it as too minor a contribution.)

@@

    \item [\done] (Review 2) Unconvinced by the motivations for the project, believes the same can be achieved in a classical framework. So maybe we should explain our motivations more clearly.

### 2025-12-03 Relations/Paper/Winter_2025_TODO.tex
Todo update

\begin{document}
\title{Summer 2025 ToDo}
\maketitle

\section*{September 2025}
\subsection*{Notes from 7th September}
Thoughts on the current state of the paper.
\begin{description}
\item[The status of wfCor]
  \begin{itemize}
    \item 
      On the ``missing'' implication isWFCor$\lnot\lnot$ to isWFminDNE$\lnot\lnot$.

      The wfCor hypothesis needs a ``choice function'' that will pick a successor $y$ of a given element $x$
      (while still refuting the given predicate).

      The property wfMinDNE$\lnot\lnot$ is equivalent to the statement that, if a $\lnot\lnot$-closed 
      predicate $P$ has no minimal element, then its complement is universally true.

      The ``no minimal element'' for not-not-closed $P$ is close to saying that its complement is coreductive; 
      the difference is precisely that between the ``strong'' existential in the coreductive statement ---
      and the weak one (with $\lnot\lnot$ applied to it) in the minimality one.

      Assuming finite branchingness and weak decidability of $P$, we could get the strong existential 
      from the weak one.  However, weak decidability and DNE are already equivalent with EM, so that 
      will only apply to decidable predicates.  There may be a relationship to isWFminEM, but that 
      would be a question for another paper.

    \item 
      On the ``strong side'' of the WF diagram, the situation is even worse.
      Neither implication between isWFCor and isWFminDNE is provable, and similarly for isWFCor and isWFSeq.

    \item 
      At this point, there does not appear to be much more to say isWFCor, so we should consider removing it.

      On Monday, we should quickly discuss the different versions of sequentially,
      and move on to writing the text of the paper.
    \end{itemize}
\end{description}

\section*{Week starting 21st April}
\begin{itemize}
  \item Items from review

  \begin{todolist}
    \item [\done] (Review 1) Elaborate on our motivations in the introduction (reviewer wasn't sure how relevant this is to ARS theory itself/ sees it as too minor a contribution.)
    \item [\done] (Review 1) Typo: incaranations $\to$ incarnations.
    \item [\done] Improve fonts for constant and text (refering to a definition on line 258). General formatting imrpovement for how we set out defns.
    \item [\done] (Review 1) Improve the layout on line 270 where we set out iiSeq. This should get fixed with an overall improvement in how we set out definitions. We should stop using itemize and verb combination.
    \item [\done] (Review 1) Typo: we obtaining $\to$ we obtain (this is in the conclusion which we want to rewrite entirely).
    \item [\done] (Review 1) Citation expansion for program=proof.
    \item [\done] (Review 2) Unconvinced by the motivations for the project, believes the same can be achieved in a classical framework. So maybe we should explain our motivations more clearly.
    \item [\done] Not convinced by our definitions, as they are imprecise and lack quantifiers.
    \item [\done] Issue with definition of R|=RP on line 188. Use of bounded is ambiguous. We should clarify which use of bounded.
    \item [\done] Improve proposition 11 on line 194, we want to make the clame that RP- $\to$ RP, and either have a one line proof or refer to the proof in Agda.
    \item [\done] Section 3 is "full of repetitions and paraphrases between the statements in natural language and corresponding formalization". We can try and think of a way to get it to flow better, we do want to provide natural language summaries of what is in the code!
    \item [\done] (Review 2) Struggled to understand the implications tables. We should add a reminder that bold font is global. We should rethink the tables generally to make them clearer. \apcomment{Don't comma seperate and don't denote counterexamples as CE-XX. ?}
    \item [\done] Struggled to find the relevant agda code for the various definitions. We should find a way to better link the two.
    \item [\done] Clarify Notation 7 on line 159: "Choose a uniform notation, X or NP, but not both".
    \item [\done] l 169: An annoying notational collision between the two arrows -> at different heights."I'm not too sure what they're referring to, though there could be some ambiguity with the arrows here, especially with use of $UN\to$.
    \item [\done] (Review 2) "l 361: Swap s(k+1) and s(k) " We should clarify the definition here otherwise people (evidently) get confused.
    \item [\done](Review 2) "l 422: $P_x$ has no arguments?"
    \item [\done] (Review 3) Check out and include the following related work:
    \begin{itemize}
        \item Christian Sternagel and René Thieman formalized results on Abstract Rewriting in Isabelle https://www.isa-afp.org/entries/Abstract-Rewriting.html
        \item André Galdino and Mauricio Ayala-Rincón also developed a theory in PVS regarding ARS and TRS  https://github.com/nasa/pvslib/tree/master/TRS
        \item What are the differences and improvements of the formalization in this paper and the ones in the literature?
        \item (Review 2) TeReSe is not state of the art. We need state of the art references. Try this: https://termination-portal.org/wiki/WScT
    \end{itemize}
    \item (Review 3) * From the formalization, the authors could explain some features and syntax of Agda for readers unfamiliar with this proof assistant. What were the main attributes of Agda that helped you in the formalization process? In line 204, the paper brings the definition of an element being finitely branching and states that the formulation of such a definition is given in line 206. FB a seems to be a set (in line 206), not a boolean. Also, in the formalization of FB a, the authors use R b a instead of R a b. What elements of Agda allow such specification capturing exactly Def. 12.
    \item [\done](Review 3) In line 270, isWFseq- is used in Section 3 but defined only in Section 5.
    \item [\done] (Review 3) In line 192, the authors state that (in TeReSe) Ind denotes BP. However, in line 186, BP is defined from an R-increasing sequence, whereas this statement is not required in the definition of Ind by TeReSe. How does this difference impact the formalizations and generalizations pointed out in Section 3.3.3? (Maybe we should explicitly address all difference with TeReSe in one location.)
  \end{todolist}

  \item Other ToDo
  \begin{todolist}
    \item [\done] Make Latex version of WF implications (initial draft).
    \item [\done] Verify which implications have and have not been formalized from the image.
    \item [\done] $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$.
    \apcomment{WFind to be removed, this is addressed in the Friday June 13th notes}
    \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
    \item [\done] (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition.
    \item [\done] Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper. I need to go through it and either understand it or come with questions to Friday's meeting.
  \end{todolist}
\end{itemize}

\section*{Week starting April 28th}
\begin{itemize}
  \item Below notes from meeting on April 25th.
  \begin{todolist}
    \item [\done] Fix Wellfounded.agda after changes made during meeting.
    \item [\done] Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper

  \end{todolist}

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item [\done] Double check the counterexamples match in the table to the diagrams.
  \item [\done] Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
  \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
  \item [\done] Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
  \item [\done] Working on CR $\to$ CP. Low priority. \apcomment{This is mentioned as one of the research items above}
\end{todolist}

\section*{Week starting 2nd June}
\begin{todolist}
  \item [\done] Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
   Transforms to
  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
  \item [\done] For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
  \item [\done] Remove "desired implications" and similar organizational issues in the code (general review)
  \item [\done] Consider defining FB in terms of existing list library; especially in the rebooted repo,
  we shouldn't use manual List type just for this.
  \item [\done] Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
  \item [\done] Revise section 3.1
\end{todolist}
\section*{Week starting 9th June (some of these items taken from Dr. Polonsky's email sent June 6th)}
\begin{todolist}
  \item [\done] Thm. 19(iv), i don't like that the parens are italicized.  maybe it would be okay if instead of CR => CP we just write "the forward implication"
  \item [\done] Proof of (iii), line 296: do we really need () around SN?
  \item [\done] Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.  Hence, the tables include a separate column for their combination.
  \item [\done] In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
(I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.  Am I missing something?). \sacomment{I don't think we need to expand that CE:3 satisfies the global hypotheses. I'm hoping that we've done enough to show to the reader how to read the table at this point. If you disagree I'm happy to add it in though. As to why have local and global counterexamples, good point. Unless either of us can think of a reason we'll remove in the next meeting.}
    \item [\done] the * and dagger in the table should be explained in the caption, or in the text.
    \sacomment{I prefer to have this as a footnote. I have put it as a caption for now but I would revert it to what we had before.  }
\end{todolist}

\subsection*{Notes from meeting on Friday June 13th}

\begin{itemize}
  \item[\done] Perhaps we should not create variations and multiple implications of WFind,
  but rather prove that it's equivalent to WFacc, but lands in a higher universe.
  Mention this once at the beginning of section 5 then proceed to analyze
  connections between WFacc and WFseq/WFmin.
\end{itemize}

\section*{July TODO}
\begin{todolist}
\item [\done] Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
\item [\done] To finish the paper: We should do a final walk through and make sure we haven't introduced errors with our edits. In particular, do all the counterexamples line up. Do all the references to different sections and pieces of code in Agda line up. 
  \item [\done] Do we remove all our local counterexamples in favour of global ones?
  \item [\done] Rework well-foundedness section 
  \item[\done]  Rework conclusion 
  \item [\done]  Rework introduction 
  \item  [\done] Do we introduce a new section for discussing Agda? Talking about why we think there is an advantage to doing this work in Agda vs (say) Isabelle

\end{todolist}

\section*{Research items}
\begin{todolist}
\item[\done] (Research item) Go deeper in the related works and see which are most relevant. Make a list of works and give summaries to be used in future papers. * Look into the literature and related works. There should be an Agda formulation of rewrite systems (check agda standard library stuff on relations). 
  \item (Research item) Find a concrete application of generalized Newman's Lemma. * Finding a term rewrite system where it's eassier to see that it is weakly cr and that every term is SM (as opposed to being CR).  
  \item (Research item) Formalize a first order term rewriting system (I can't remember what the motivation for this was). Use TeReSe to create a list of rewrite systems.
  \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counerexamples been shown before?
  \item (Research item) Work on the missing implicaitons from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
  \item (Research item) Do we want to reincorporate Knaster Tarski? - Not this paper 
  \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution. - Not this paper
  \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle. 
  \end{todolist}

\section*{Agda standard library}
Some of the work we have explored is formalized in the Agda standard library.  
% https://agda.github.io/agda-stdlib/v1.7.3/Relation.Binary.Rewriting.html#2096
\begin{todolist}
\item[\done] Write about the standard library formalization in our paper and talk about how ours differs. 
\item[X]  Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluet, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
  \item Investigate contributing work to the ASL. This may mean refactoring the work already done to conform with the ASL. Specific contributions would likely be: Generalized NL. Theorem's 122 and 123. Alternative definitions of Wellfounded, the implications for the hierarchy.
\end{todolist}

\section*{20th August todos}
\begin{todolist}
  \item [\done] (Secondary) Find consistency with NP and UN with respect to reduction and conversion. Should the default be by reduction for both. Should we be explicit with $\to$ and = in each case.  \sacomment{Main issue here is that we'll either introduce an inconsistency with our code or we'll have a hard to read symbol. We can do $\to$ as super or sub-script in Agda. If we're happy with $NP\to$ in agda but using a different script in the paper then I think we should go ahead and be explicit for both UN and NP as to whether it is WRT conversion or reduction. We already have this inconsistency in the code with $UN\to$} \apcomment{In the agda code let's not use arrow and have arrow implied as default but be explicit with '=' sign.}
  \item [\done] Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex. \sacomment{Done with the exception of WFseq-. This needs a bit more thought. Similarly for the relation between WFcor and WFminCor.}
  \item [\done] Make a decision regarding WFcor. We use it to imply WFacc using AccCor. But otherwise it is sort of orphaned off. Does it help contribute to the overall story? \sacomment{We've now related it to WFmin by requiring that correductive predicates have double negation elimination. Is this too strong a requirement? Similarly we have linked WFacc to WFcor but this proof requires the same property as well as limiting ourselves to accessible predicates. Again, is this too much?}
  \item [\done] Get the classical hypothesis and relations organized and see how they're used in the implications (organize implications by classical requirement. In the implications file we can import the classical implications. Basically, refactor the code.) \sacomment{Done but could be further refactored.}
  \item [\done] Make a cheat sheet for the next meeting regarding to talk about coreductive. How it relates on the weak side and on the strong side. SEQ seq+- , how to present these. Try and clarify what the issues are here and what exactly are the differences between them in terms of definition and implication. Could one be removed and the overall story stay the same? \sacomment{Regarding seq+ (and seq+-) we currently only show that seq+ implies seq and seq+- implies seq- so could be removed without changing any of our other implictions.} 
\end{todolist}

\section*{September 15th todo}
\begin{todolist}
\item[\done] (Minor) We want to have a sentence in our WF section making clear that we can consider local properties as well and maybe make an example from accessible to sequential. 
  \item[\done] Sentence explaining that wfacc is equivalent to wfind and therefore isn't included in the diagram (wfind).
\end{todolist}

\section*{September 26th TODO}
\begin{todolist}     
\item[\done] Focus for next meeting on writing. 
  \item [\done] Are not not closed predicates over natural numbers dedcidable: If not is this a counterexample for WFminDNE.
\end{todolist}

\section*{October 10th TODO}
\begin{todolist}     
\item[\done] Want to show that FB and weak decidability gives us accCor (think we may have shown this previously)
  \item[\done] Add 'is' to wfcor macros.
  \item[\done] make a decision on wfseq not not name. 
  \item[\done] Keep on cleaning the WF section in paper. 
\end{todolist}

\section*{October 15th TODO / Oct 22nd}
\begin{todolist}     
  \item It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item [\done] Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
  \item [\done] Do we want to keep anything in the old/delete section of WF?
  \item [\done] Do we want to add anything about counter examples or positive examples? 
  \item [\done] We may want to use words rather than macros in certain locations
  \item [\done] Check through the comments in general in the section. 
\item [\done]  CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
\item [\done]  Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
\item [\done]  Use of macros in WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
\item Does WFseq- with MP== imply WFseq? (W're thinking it will need rdec as well to give us the implication).
\item [\done] make the WF macro bold font?
\item add wfseq not not to the definitions?
\item [\done] Go through the bibliography links. Not all of them are currently working!
\item We want to start looking at examples. What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties. E.g. lambda calculus satisfies some of our classical properties. As does first order term rewrite system. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
\item [\done] Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
\item [\done] We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
\item [\done] Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
\item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide. First order term rewrite systems are (always?) fb and R is dec. 
\item [\done] Change the macro for FB so that it is also boldface
\item [\done, did SN to WN instead] update wfcounters to show that asserting wfmin implies the excluded middle (and wfmindne the weak excluded middle).
\item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle).

\end{todolist}

\section*{Plan for PLDI submission}
\begin{todolist}
  \item[X] Aim for first draft finished by the end of the 29th.
  \item[\done] Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
  \item [\done] discussion env has qed boxes which shouldn't be there.
  \item[\done] from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
  Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!) 
  \item [\done] Make consistent how we display definitions. 
  \item [\done] Work on the conclusion
  \item [\done] Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
  \item [\done] Check the PLDI page for submission rules/requirements. In particular the bibliography style 
  \item [\done] Run through and compile everything, make sure we didn't introduce any bugs
  \item [\done] Check the layout of figures through the paper. Counterexamples for example is currently `off'.
  \item [\done] talk about why we use agda in 1.2 Agda is the perfect system for formalizing programming language theory.  
  \item Submit 
  \item [\done] Add a paragraph or two giving a short overview/summary of Agda.
  \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
  \item Consider adding some more motivations 
  \item Look at the seq-minus vs. seq-not-not issue 
  \item Final read through (wed?)
  \item [\done] make an external bibliography file rather than inlining in main file. Make sure bibliography is up to standard (e.g. emph on book title).
  \item Submission deadline is Thursday 13th 
\end{todolist}

\section*{Post pldi todos}
\begin{todolist}
  \item Make the well founded definitions conform to the style of the definitions in other sections. Namely, bring the symbols to the start of the sentence. Use bemph where appropriate. Do we want all definitions to be itemized?
  \item Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise). Chat makes the following suggestion (see commented out line in tex file):
  % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
  \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
  \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
  \item Go through the code, make naming consistent and self-documenting
  \item run through the table again and check the counterexamples line up. 
  \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code). Similarly it should be the double arrow iff. Check through paper for similar changes.

\end{todolist}

notes to self:
- Tell Dr. P to check out the trs pvs paper.

\end{document}

>>>>

\begin{document}
\title{Winter 2025 ToDo}
\maketitle

\section*{December 2025}
\subsection*{Carry over from previous TODO}
\begin{todolist}
    \item (Review 3) * From the formalization, the authors could explain some features and syntax of Agda for readers unfamiliar with this proof assistant. What were the main attributes of Agda that helped you in the formalization process? In line 204, the paper brings the definition of an element being finitely branching and states that the formulation of such a definition is given in line 206. FB a seems to be a set (in line 206), not a boolean. Also, in the formalization of FB a, the authors use R b a instead of R a b. What elements of Agda allow such specification capturing exactly Def. 12.
    \item  Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluent, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
  \item Investigate contributing work to the ASL. This may mean refactoring the work already done to conform with the ASL. Specific contributions would likely be: Generalized NL. Theorem's 122 and 123. Alternative definitions of Well-founded, the implications for the hierarchy.
  \item  It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item Is there a path from WFseq- with MP== to WFseq? (W're thinking it will need rdec as well to give us the implication
  ).
 \item incorporate wfseq not not to the paper?
 \item We want to start looking at examples. What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties. E.g. lambda calculus satisfies some of our classical properties. As does first order term rewrite system. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
 \item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide. First order term rewrite systems are (always?) fb and R is dec. 
  \item Make the well founded definitions conform to the style of the definitions in other sections. Namely, bring the symbols to the start of the sentence. Use bemph where appropriate. Do we want all definitions to be itemized?
  \item Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise). Chat makes the following suggestion (see commented out line in tex file):
  % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
  \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
  \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
  \item Go through the code, make naming consistent and self-documenting
  \item run through the table again and check the counterexamples line up. 
  \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code). Similarly it should be the double arrow iff. Check through paper for similar changes.

\end{todolist}
\section*{Research items}
\begin{todolist}
  \item (Research item) Find a concrete application of generalized Newman's Lemma. * Finding a term rewrite system where it's easier to see that it is weakly cr and that every term is SM (as opposed to being CR).  
  \item (Research item) Formalize a first order term rewriting system. Use TeReSe to create a list of rewrite systems.
  \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counterexamples been shown before?
  \item (Research item) Work on the missing implications from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
  \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle. 
  \end{todolist}
\end{document}
